Towards Transparency and Open Science

### 2023-02-01 manuscript.Rmd
preregistration in regard of transparency
changed as means of for in regard of

<!--how it relates to the articles-->
Based on this distinction, the articles answer the second question (the *how*).
I argue that transparency in statistical methods is enabled by computational reproducibility, while transparency about sociological factors is facilitated by preregistration.
The conceptualization of computational reproducibility and preregistration as means for transparency is supplemented by practical guidance on how researchers may implement these approaches.

>>>>

<!--how it relates to the articles-->
Based on this distinction, the articles answer the second question (the *how*).
I argue that transparency in statistical methods is enabled by computational reproducibility, while transparency about sociological factors is facilitated by preregistration.
The conceptualization of computational reproducibility and preregistration in regard of transparency is supplemented by practical guidance on how researchers may implement these approaches.
